### 2020-01-09 nlp_models.tex
more to nlp added

>>>>

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|c|c|c|c|}
\hline
   &    & Frobenius Norm & Spectral Norm & Weighted Alpha & Alpha-Norm \\
 Series & \#Layers   & $\Vert\mathbf{W}\Vert_{F}$ & $\Vert\mathbf{W}\Vert_{\infty}$ & $\hat{\alpha}=\alpha\log\lambda_{max}$ & $\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}$ \\
\hline
 GPT & & & & \\
 GPT2 (small) & & & & \\
 GPT2-medium & & & & \\
 GPT2-large & & & & \\
 GPT2-xls & & & & \\

\hline
\end{tabular}
\end{center}
\caption{Average metrics for pretrainnd OpenAI GPT and GPT2 models.}
\label{table:models}
\end{table}
